Provenance analysis

### 2021-08-06 analysis/provenance2.Rmd
Provenance tags

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    caller_expression,
    provenance, # the main provenance (i.e. climbing up LHSs)
    provenance_args,
    nb_provenances,
    nb_operations,
    longest_path_size,
    all_provenances
  ) -> E_prov

@@

# Provenance in numbers of calls

```{r}
provenance_calls <- E_prov %>% count(provenance, wt = duplicates, sort = TRUE) %>% 
  mutate(pc = 100 * n / sum(n), cpc = cumsum(pc))

nrows <- min(10, nrow(provenance_calls))
r_vec("nb provenance calls", nrows, provenance_calls$provenance)
r_vec("percent provenance calls", nrows, provenance_calls$pc)
r_vec("cumpercent provenance calls", nrows, provenance_calls$cpc)
```

@@

# Provenance in number of sites

@@

>>>>

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    ev_class = expr_resolved_class, # S3/S4 class
    caller_expression,
    provenance, # the main provenance (i.e. climbing up LHSs)
    provenance_args,
    nb_provenances,
    nb_operations,
    longest_path_size,
    all_provenances
  ) -> E_prov

@@

# Provenances using the representative provenance

## Provenance in numbers of calls

```{r prov_number_calls}
provenance_calls <- E_prov %>% count(provenance, wt = duplicates, sort = TRUE) %>% 
  mutate(pc = 100 * n / sum(n), cpc = cumsum(pc))

nrows <- min(10, nrow(provenance_calls))
r_vec("nb provenance calls", nrows, provenance_calls$n)
r_vec("percent provenance calls", nrows, provenance_calls$pc)
r_vec("cumpercent provenance calls", nrows, provenance_calls$cpc)
```

@@

## Provenance in number of sites

```{r prov_number_sites}
provenance_sites <- E_prov %>% group_by(src_ref) %>%
  summarize(provenance = paste0(sort(unique(provenance)), collapse = "; "), n_provs = n_distinct(provenance)) %>% 
  count(provenance, sort = TRUE) %>% 
  mutate(pc = 100 * n / sum(n), cpc = cumsum(pc))

# To get to 85 %

nrows <- min(14, nrow(provenance_sites))
r_vec("provenance name", nrows, if_else(provenance_sites$provenance == "", "NA", provenance_sites$provenance))
r_vec("nb provenance sites", nrows, provenance_sites$n)
r_vec("percent provenance sites", nrows, provenance_sites$pc)
r_vec("cumpercent provenance sites", nrows, provenance_sites$cpc)

`r datatable(provenance_sites)`

@@

# Classes

## In number of calls

```{r class_nb_calls}
classes_calls <- E_prov %>% count(ev_class, wt = duplicates, sort = TRUE) %>% 
  mutate(pc = 100 * n / sum(n), cpc = cumsum(pc))

## In number of sites

```{r class_nb_sites}
classes_sites <- E_prov %>% group_by(src_ref) %>%
  summarize(ev_class = paste0(sort(unique(ev_class)), collapse = "; "), n_classes = n_distinct(ev_class)) %>% 
  count(ev_class, sort = TRUE) %>% 
  mutate(pc = 100 * n / sum(n), cpc = cumsum(pc))
